Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-20 presentation.qmd
fix val sample sizes

val_o_win_prop_const <- val_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 1)
```

>>>>

val_o_win_prop_const <- val_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 0.1)
```
